The Quantum Sneakernet

### 2019-01-16 Simon's section/main.tex
Simons sec: formatting, spelling, figs to PDF

\documentclass[aps,prl,twocolumn,10pt,nofootinbib]{revtex4}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

@@

%\begin{abstract}
%Your abstract.
%\end{abstract}
Reliable, fast, long distance communication has always been a driver of technological and economic progress for humanity.  Whether couriers on foot or horseback, carrier pigeons, smoke signals, semaphores or electronic and optical signals, humanity has continually refined technology to make long distance communications easier, faster, cheaper and more reliable.  We now live in a world where near light speed, global communications is universally available and for a significant fraction of human population, accessible with a device that lives in our pockets.  
\\
\\

@@

\\
\\
{\bf If we had the ability to redesign the classical internet from scratch, how would we do it?}
\\
\\
The hardware that will be needed to transmit quantum information around the globe will be a parallel network to the classical internet as at the very least a fast classical network is still needed to relay the required information to make any quantum communications channel work \cite{?}. So, at a minimum, we can conclude that a global quantum network will be {\em rate limited} by the classical networking infrastructure that supports it.  However, considering that the classical internet currently has the capacity to transmit information at approximately 70\% of the speed of light (in standard silica fiber optics), over global distances and can do so at extremely high data rates means that we will have to work very hard to design and build large-scale quantum networks before the classical side-channel produces any significant bottlenecks.  
\\
\\
There have been traditionally three major candidate techniques to distribute quantum information over a long distance communications channel:
\begin{itemize}
\item Optic fibre transmission and quantum repeaters \cite{?}.
\item Direct free space transmission \cite{?}.
\item Quantum satellites \cite{?}. 
\end{itemize}
Each of these techniques use photons as the carrier for quantum information and have been used already as a transmission mechanism for quantum key distribution (QKD) protocols \cite{?}.   However, there are several issues with these techniques that could make building a global quantum network difficult.  
\\
\\
While QKD remains the primary protocol implemented on current quantum communication hardware, a true global internet needs to handle a vast array of potential applications, including connecting together fully error-corrected quantum computing systems \cite{?}.  Consequently, we need to consider several metrics in a potential hardware implementation.  Four primary metrics can be identified:
\begin{itemize}
\item Speed:  How many qubits of quantum information can we transmit in a second?
\item Distance: How far can we transmit qubits while maintaining a desired speed?
\item Fidelity: How accurately can we transmit each qubit while maintaining the speed and distance required?
\item Cost: What will it cost us to build, deploy and maintain the hardware for a quantum channel of a given speed, distance and fidelity?
\end{itemize}
We want to maximise the first three metrics as much as physically possible, while minimising the fourth.  Classical networks provides an upper bound of the speed and distance of a possible global quantum network, and fidelity is ultimately bounded by the intended application of the network, with QKD providing a useful lower bound (as key distribution can be performed with low fidelity transmission) and connecting together fully error-corrected quantum computers running large quantum algorithms are a useful upper bound (requiring channel fidelities arbitrarily close to one). 
\\
\\
In this chapter we discuss some of the practical needs that need to be taken into account when developing a quantum network -- in the context of quantum key distribution -- and introduce a fourth type of model for global quantum networking; the quantum sneakernet.  We will take a qualitative look at its structure and operation and argue that there are many potential practical and economic benefits to using this particular method as a primary trunk line technology for long-range, fast and high fidelity quantum communications over global distances.

\section{Public-Key Cryptography}

Public-key is a method of encryption that utilizes an asymmetric process based on the assumed difficulty of certain mathematical problems.  Probably the most well-known protocol, RSA, is based on the difficulty of factoring large composite numbers into their prime components \cite{?}. 
\\
\\
Thus far, public-key cryptography has seen its most successful adoption in the online space, where cryptographic security is needed for many sensitive tasks: online banking, shopping email and messaging.  
\\
\\
Public-key cryptography uses two keys that are related through a asymmetric mathematical function.  A asymmetric function in this context is a problem that is very easy to solve in one direction, such as multiplying two large prime numbers together, but extremely difficult to do in reverse (finding the prime factors of a large composite number).  One of the two cryptographic keys is published openly and used by a sender to encrypt a message.  The other key is held in secret by the receiver and is needed to decrypt the message.  Unless an adversary has the ability to solve the difficult underlying mathematical problem, the message cannot be decrypted without the private-key.  
\\
\\
While public-key encryption has been widely adopted across the world, it is not considered information-theoretically secure due to the {\em assumed} difficulty of the underlying mathematical problem.  In the case of RSA and prime factorization, we don't fully understand the computational difficulty 
of the factoring problem, and can therefore not guarantee that RSA will not be broken tomorrow by some brilliant computer scientist or mathematician.  
\\
\\
Quantum computing adds a whole new level of security problems to public-key cryptography. It has been shown that, if an adversary has access to a large quantum computer, the mathematical problems underlying public-key cryptography {\em can be solved efficiently}.  Shor's algorithm, unarguably the most famous quantum algorithm, kick-started the first acceleration of quantum computing development in 1994.  Shor demonstrated that both the factoring and discrete log problems could be solved using a polynomially increasing number of quantum bits (qubits) as the problem size increases \cite{?}.  This effectively makes a large number of public-key crypto-protocols obsolete if quantum computers could ever be built.  Consequently, {\em any} sensitive information transmitted using public-key cryptosystems has to be assumed compromised by the most hardened security experts, even though quantum computers capable of breaking public-key cryptosystems do not yet exist.

\section{The Problem of Long-Term Storage}
The problem is more pronounced with information that requires long-term security after its initial transmission.  This may include national security secrets, trade or business secrets or personal information such as medical and banking records.  The risk when transmitting this kind of information is that its value may not be related to how quickly it can be decrypted, but instead whether it can be decrypted at all.  It is well known that intelligence operations (both by governments, private sector actors or nefarious organizations) routinely intercept encrypted traffic on classical networks and simply put it into long-term storage, hoping that, some day in the future, technology progresses to the point where the information can be decrypted and exploited.  
\\
\\
It is this kind of information that is particularly vulnerable to quantum computers.  If data is encrypted using protocols that are susceptible to quantum attacks, eventually this information will become exposed.  If secrecy needs to be maintained many years in the future (which is certainly the case for much national security, trade secrets, business secrets and personal information), this is a significant problem -- one that does not yet have a satisfactory solution beyond either preventing the encrypted information from being intercepted in the first place or crossing our fingers that quantum technology will either not be built or only be available forever to friends and allies.   
\\
\\
One phrase that floats around the community more and more is "post-quantum cryptography".  It is a term used to describe any classical cryptographic technique that is based on mathematical problems that can be proved to be {\em not efficiently solvable by quantum computers.}  While research is still ongoing, there have been no significant results suggesting such a crypto scheme exists.  Consequently, utilization of such schemes cannot be guaranteed to be secure into the future, especially if one believes that large-scale quantum computing is a technological innevitability.

\section{One-time pads and key exchange over a network}
The concept of informationally secure cryptographic schemes dates back to the late 19th century.  Initially developed by Frank Miller in 1882 \cite{?} and re-invented in 1917 \cite{?}, it wasn't until the 1940's that Claude Shannon actually theoretically proved the power of this technique to completely secure a transmitted message \cite{?}.  To this day, one-time pads remain the only officially provable informationally secure protocol for cryptography.  
\\
\\
This protocol is a method to encrypt information such that, {\em if implemented perfectly} (and this is where we actually get into trouble), can never be broken.  The laws of the universe and reality itself guarantee that an adversary without access to the encryption key {\em can never}, regardless of any hypothetical computational power (quantum, classical or anything else) decrypt the message. Informationally secure protocols are the holy grail of network and information security and are of huge relevance to almost all aspects of digital life in the twenty-first century. Unfortunately, as with most things in the real world, the devil is in the details: The caveat of {\em perfectly implemented} is essentially a practical impossibility.  
\\
\\
The basic principles and core assumptions of one-time-pad encryption are:
\begin{itemize}
\item The sender (conventionally referred to as Alice) and receiver (Bob) both have access to a shared key that is completely random. Here we mean "random" in the information-theoretic sense of the word in that the bit strings have maximum Shannon entropy (although even this is not possible without an infinite bit string). This key has exactly same length as the message to be transmitted.
\item The key that Alice and Bob share cannot have been compromised in any way,  i.e. no adversary can have any information about any part of the random bit string shared between Alice and Bob at any time.
\item This key is used once {\em and only once} to encrypt a single message.  The key or any part of the key can never be used to encrypt two separate transmissions.
\end{itemize}

If these three core points are adhered to, the encrypted message is completely unbreakable by any adversary who may intercept it, regardless of any hypothetical computational resources they may have. Unfortunately, the above conditions are simply not practical in most real world situations.  
\begin{itemize}
\item Generating a random bit string, in the true definition of random, has only become technologically possible in the past decade or two as result of quantum technology.  Quantum random number generators use the intrinsic randomness of quantum mechanical processes to generate random bit strings that for all intents and purposes are sufficient for one time pads.  These devices can now be bought as off the shelf units with varying degrees of quality.  
\item Avoiding the reuse of a key can, in principle, be adhered to; but satisfying this requirement may be economically or logistically impractical.  Avoiding reuse becomes even more difficult when the message to be encrypted is big.  There are many examples of technology in the field that require secure, high data-rate transmission.  Video footage from helicopters or drones is a good example.  A drone equipped with a high-resolution 4K camera system needs to be able to transmit information at a rate of 764 GB/hour uncompressed.  This would require the same rate of one-time-pad material to be generated and shared between Alice and Bob to ensure a secure connection of the video stream.  None of this material could be used even a second time.  
\item The third and most vulnerable constraint is the sharing of key information between Alice and Bob in a manner that can be guaranteed to have never been compromised.  This is complicated by the fact that Alice and Bob in almost all practical situations will not be in physical contact with each other prior to sharing an encrypted message.  How can we exchange a large amount of key material between two parties who have never met in such a way that we can be as certain as humanly possible that the key information was not revealed, sold, copied or otherwise accessed by a third party?  The third party may even be authorized to have access to the key information.  This would immediately destroy the {\em perfectly implemented} assumption underlying the security of the one-time-pad.  
\end{itemize}

While many crypto-systems are not based on one-time-pad encryption because of these constraints, the sharing of cryptographic keys is still of major concern.  Transmitting  keys over {\em any} publicly accessible network is fraught with security problems as there is no way of encrypting the key material without then asking how the keys used to encrypt the keys are shared.
\\
\\
For extremely sensitive tasks, key-exchange and security is usually achieved through some combination of segregated networking and obfuscation. Here are some examples:

\subsection{Security through obfuscation}
Some techniques for key and message exchange attempt to hide from adversaries any evidence that such protocols are taking place.  This may be as simple as giving a secret key or message to a 20-something hipster riding a bike instead of man in a well-tailored suit with dark sunglasses and a briefcase handcuffed to his wrist.  Security through obfuscation is more focused on not arousing suspicion or misdirecting adversaries to use a false attack vector when attempting to compromise information exchange, rather than directly defending against a potential attack.

\subsection{Security through segregated networks}

Segregating classical networks from the public and/or potential adversaries is a more common technique simply because the speed and range of radio signals and optic fiber technology is so large.  Ensuring that a military or intelligence network is not connected to anything that is more widely accessible, in principle, allows for a higher level of security and the ability to have confidence that cryptographic keys can be sent without interception.   
\\
\\
These basic techniques are rarely implemented in isolation.  Complex network security uses many combinations of good encryption, segregated networks, obfuscation and other techniques to lower the probability of compromised data transmission.  However, none of these techniques fully satisfy the assumptions of an information-theoretically secure cryptographic protocol, and they often rely heavily on the honesty and competence of human personnel in order to be implemented effectively.  
\\

\section{QKD versus classical key exchange techniques}

A 2016 assessment from the UK agency GCHQ references four concerns with QKD (Quantum Key Distribution) as an effective replacement for classical techniques.  
\\
\\
These concerns are:
\begin{itemize}
\item {\em QKD protocols address only the problem of agreeing on keys for encrypting data.} Ubiquitous on-demand modern services (such as verifying identities and data integrity, establishing network sessions, providing access control, and automatic software updates) rely more on authentication and integrity mechanisms — such as digital signatures — than on encryption.
\item {\em The two major functional limitations of commercial QKD systems are the relatively short effective range of transmission and the fact that BB84 and similar proposals are fundamentally point-to-point protocols.} This means that QKD does not integrate easily with the Internet or with the mobile technologies, apps and services that dominate public and business life today.
\item {\em Hardware is relatively expensive to obtain and maintain.} Unlike software, hardware cannot be patched remotely or cheaply when it degrades or when vulnerabilities are discovered.
\item {\em Any real-world QKD system will be built from classical components, such as sources, detectors, fibers, and ancillary classical network devices, any one of which may prove to be a weak link.}  A number of attacks have been proposed and demonstrated on deployed QKD systems that subvert one of more of these hardware components, enabling the secret shared key to be recovered without triggering an alarm.
\item {\em Denial of service (DoS) attacks that interfere with the paths carrying the QKD transmissions also seem potentially easier with QKD than with contemporary Internet or mobile network technologies.} Since QKD devices typically abort a key establishment session when they detect tampering, this makes it difficult to recommend QKD for contexts where DoS attacks are likely to be attempted.
\end{itemize}

As we will describe, a sneakernet based system can address each of these concerns or significantly mitigate these chief concerns of a quantum-based key distribution network.

\section{Trusted couriers and one-time-pads}

Before detailing the specifics of a sneakernet based entanglement distribution network, let us first discuss the general framework that this system leverages in the context of key distribution and encryption.  This is the principle of physical trusted couriers and one-time-pads.  This general technique, utilised routinely for extremely sensitive key exchange, does not transmit key material over any classical network and instead entrusts a physical courier with pre-loaded key material on a portable memory stick.  
\\
\\
The key material, which is generated at home base, is physically couriered to its destination and security is, in principle, achieved using a combination of obfuscation, deception and the trust of the courier.  The couriers themselves can be heavily vetted, achieving the highest levels of security clearance within an organisation and dummy key material may be given to couriers at random to see if it is showing up in places where it is not supposed to.  
\\
\\
Today's technology makes the other requirements -- easy access to high capacity storage and one-time-pad material of sufficient quantity to encrypt the largest-data-rate applications -- straightforward to achieve. Consequently, distribution of the key material itself is typically the hardest assumption to satisfy when relying on the information-secure nature of one-time-pads.
\\
\\
A quantum sneakernet is a technological solution to the problem of having to trust the courier.  We exploit the nature of quantum to develop an analogue of the trusted-courier network wherein the human couriers are no longer a weak link.

\section{An active quantum memory unit}
The key technology for a quantum sneakernet is the fabrication and packaging of a long-lived {\em active} quantum memory.  Quantum memories are inherently fragile due to quantum decoherence induced via uncontrollable interactions with the wider environment.  Today's best physical qubits typically have lifetimes of the order of one millisecond. While there has been significant research into finding or engineering quantum systems with lifetimes of seconds or minutes, these systems are hard to control (i.e. difficult to read in/out actual quantum information) because they have been engineered to be so isolated from the environment that the control signals required to load, manipulate or measure quantum information are difficult to implement.  The ability to build quantum technology that is useful in the field requires increasing the effective memory time -- the lifetime of data stored as qubits -- so that they can be used on timescales relevant to human manipulation.  
\\
\\
The problem of increasing the effective lifetime of qubit information was solved with the formulation of active quantum error correction (QEC) protocols.  QEC utilizes redundant encoding, wherein a single {\em logical} qubit of quantum information is encoded using a finite number of {\em physical} qubits.  Continuous operations on this array of physical qubits are used to extract information regarding physical errors; and, provided physical error rates are sufficiently low, the logically encoded information can be preserved for an arbitrary amount of time.  Unlike specially engineered quantum systems that are isolated to achieve long memory times, these encoded memories consist of intrinsically unstable physical qubits.  However, encoded information in the system is maintained for arbitrary timescales via active QEC.  Active quantum memories form the foundational building blocks of a quantum sneakernet network, allowing us to maintain encoded quantum information for long periods -- even decades -- indeed, times long enough for most important real-world applications.  
\\
\\
The second major element to a sneakernet network is {\bf PORTABILITY}.  The underlying qubit technology has to be amenable to constructing active quantum memories that can be packaged and physically moved from place to place.  
\\
\\
If we consider the six major {\em qubit} technologies that are the most developed and have been most successful in attracting significant private/public sector investment, we see consider some of the pros and cons.  In a lot of systems, {\em infrastructure requirements} appears to be the biggest barrier to portability.  
\begin{itemize}
\item {\bf Superconducting qubits} require operational temperatures of approximately 30mK in order to maintain operational coherence.  This temperature requires dilution refrigeration technology which is difficult to make portable.  
\item {\bf Ion-Traps} require an almost perfect vacuum environment which again may prove to be problematic. 
\item {\bf Linear optical technology}: Can avoid infrastructure issues such as vacuums and extremely low temperatures.  However, the probabilistic gates in linear optics and the consequently, ability to create active error corrected logical qubits has some practical issues to still overcome.    
\item {\bf Quantum Dots}: Similar to superconducting technology -- dilution refrigeration technology is required.
\item {\bf Phosphorus in Silicon}: Similar to quantum dots and superconductors -- dilution refrigeration technology is required. 
\item {\bf Colour centers, e.g. NV-diamond}:  Vacuums and dilution refrigeration technology not required.  
\end{itemize}

>>>>

\documentclass[twocolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-2}

\usepackage[pdftex]{graphicx}
\usepackage[usenames, dvipsnames, svgnames, table]{xcolor}
\usepackage{mathrsfs}
\usepackage[colorlinks, breaklinks]{hyperref}
\usepackage{url}
\usepackage{makeidx}
\usepackage{nomencl}
\usepackage{colortbl}
\usepackage[section]{placeins}
\usepackage{qcircuit}
\usepackage{array}
\usepackage{amsmath}
\usepackage[noend]{algpseudocode}
\usepackage{mdframed}
\usepackage{type1cm}
\usepackage{lettrine}
\usepackage{afterpage}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage{multirow}
\usepackage[margin=0pt, font=small, labelfont=bf, labelsep=endash, justification=centerlast, labelsep=colon]{caption}
\usepackage[colorinlistoftodos]{todonotes}

\newcommand{\sectionby}[1]{\begin{center}\textit{--- by #1.}\end{center}}
\newcommand{\famousquote}[2]{\noindent\textit{``#1"} --- #2.\index{Quotes}\index{#2}}
\newcommand{\dropcap}[2]{\lettrine[lines=2, findent=3pt, nindent=0pt]{#1}{#2}}

@@

\tableofcontents

\section{The quantum Sneakernet\texttrademark}\index{Sneakernet}\label{sec:sneakernet}

\sectionby{Simon Devitt}

\dropcap{R}{eliable}, fast, long distance communication has always been a driver of technological and economic progress for humanity. Whether couriers on foot or horseback, carrier pigeons, smoke signals, semaphores or electronic and optical signals, humanity has continually refined technology to make long distance communications easier, faster, cheaper and more reliable. We now live in a world where near light speed, global communications is universally available and for a significant fraction of human population, accessible with a device that lives in our pockets.

@@

\textbf{If we had the ability to redesign the classical internet from scratch, how would we do it?}

The hardware that will be needed to transmit quantum information around the globe will be a parallel network to the classical internet as at the very least a fast classical network is still needed to relay the required information to make any quantum communications channel work \cite{?}. So, at a minimum, we can conclude that a global quantum network will be \textit{rate limited} by the classical networking infrastructure that supports it. However, considering that the classical internet currently has the capacity to transmit information at approximately 70\% of the speed of light (in standard silica fibre optics), over global distances and can do so at extremely high data rates means that we will have to work very hard to design and build large-scale quantum networks before the classical side-channel produces any significant bottlenecks.

There have been traditionally three major candidate techniques to distribute quantum information over a long distance communications channel:
\begin{itemize}
\item Optic fibre transmission and quantum repeaters \cite{?}.
\item Direct free space transmission \cite{?}.
\item Quantum satellites \cite{?}. 
\end{itemize}
Each of these techniques use photons as the carrier for quantum information and have been used already as a transmission mechanism for quantum key distribution (QKD) protocols \cite{?}.  However, there are several issues with these techniques that could make building a global quantum network difficult.

While QKD remains the primary protocol implemented on current quantum communication hardware, a true global internet needs to handle a vast array of potential applications, including connecting together fully error-corrected quantum computing systems \cite{?}. Consequently, we need to consider several metrics in a potential hardware implementation. Four primary metrics can be identified:
\begin{itemize}
\item Speed: How many qubits of quantum information can we transmit in a second?
\item Distance: How far can we transmit qubits while maintaining a desired speed?
\item Fidelity: How accurately can we transmit each qubit while maintaining the speed and distance required?
\item Cost: What will it cost us to build, deploy and maintain the hardware for a quantum channel of a given speed, distance and fidelity?
\end{itemize}
We want to maximise the first three metrics as much as physically possible, while minimising the fourth. Classical networks provides an upper bound of the speed and distance of a possible global quantum network, and fidelity is ultimately bounded by the intended application of the network, with QKD providing a useful lower bound (as key distribution can be performed with low fidelity transmission) and connecting together fully error-corrected quantum computers running large quantum algorithms are a useful upper bound (requiring channel fidelities arbitrarily close to one).

In this chapter we discuss some of the practical needs that need to be taken into account when developing a quantum network -- in the context of quantum key distribution -- and introduce a fourth type of model for global quantum networking; the quantum Sneakernet. We will take a qualitative look at its structure and operation and argue that there are many potential practical and economic benefits to using this particular method as a primary trunk line technology for long-range, fast and high fidelity quantum communications over global distances.

\subsection{Public-key cryptography}

Public-key is a method of encryption that utilises an asymmetric process based on the assumed difficulty of certain mathematical problems. Probably the most well-known protocol, RSA, is based on the difficulty of factoring large composite numbers into their prime components \cite{?}.

Thus far, public-key cryptography has seen its most successful adoption in the online space, where cryptographic security is needed for many sensitive tasks: online banking, shopping email and messaging.

Public-key cryptography uses two keys that are related through a asymmetric mathematical function. A asymmetric function in this context is a problem that is very easy to solve in one direction, such as multiplying two large prime numbers together, but extremely difficult to do in reverse (finding the prime factors of a large composite number). One of the two cryptographic keys is published openly and used by a sender to encrypt a message. The other key is held in secret by the receiver and is needed to decrypt the message. Unless an adversary has the ability to solve the difficult underlying mathematical problem, the message cannot be decrypted without the private-key.

While public-key encryption has been widely adopted across the world, it is not considered information-theoretically secure due to the \textit{assumed} difficulty of the underlying mathematical problem. In the case of RSA and prime factorisation, we don't fully understand the computational difficulty of the factoring problem, and can therefore not guarantee that RSA will not be broken tomorrow by some brilliant computer scientist or mathematician.

Quantum computing adds a whole new level of security problems to public-key cryptography. It has been shown that, if an adversary has access to a large quantum computer, the mathematical problems underlying public-key cryptography \textit{can be solved efficiently}. Shor's algorithm, unarguably the most famous quantum algorithm, kick-started the first acceleration of quantum computing development in 1994. Shor demonstrated that both the factoring and discrete log problems could be solved using a polynomially increasing number of quantum bits (qubits) as the problem size increases \cite{?}. This effectively makes a large number of public-key crypto-protocols obsolete if quantum computers could ever be built. Consequently, \textit{any} sensitive information transmitted using public-key cryptosystems has to be assumed compromised by the most hardened security experts, even though quantum computers capable of breaking public-key cryptosystems do not yet exist.

\subsection{Long-term storage}

The problem is more pronounced with information that requires long-term security after its initial transmission. This may include national security secrets, trade or business secrets or personal information such as medical and banking records. The risk when transmitting this kind of information is that its value may not be related to how quickly it can be decrypted, but instead whether it can be decrypted at all. It is well known that intelligence operations (both by governments, private sector actors or nefarious organisations) routinely intercept encrypted traffic on classical networks and simply put it into long-term storage, hoping that, some day in the future, technology progresses to the point where the information can be decrypted and exploited.

It is this kind of information that is particularly vulnerable to quantum computers. If data is encrypted using protocols that are susceptible to quantum attacks, eventually this information will become exposed. If secrecy needs to be maintained many years in the future (which is certainly the case for much national security, trade secrets, business secrets and personal information), this is a significant problem -- one that does not yet have a satisfactory solution beyond either preventing the encrypted information from being intercepted in the first place or crossing our fingers that quantum technology will either not be built or only be available forever to friends and allies.

One phrase that floats around the community more and more is `post-quantum cryptography'. It is a term used to describe any classical cryptographic technique that is based on mathematical problems that can be proved to be \textit{not efficiently solvable by quantum computers.} While research is still ongoing, there have been no significant results suggesting such a crypto scheme exists. Consequently, utilisation of such schemes cannot be guaranteed to be secure into the future, especially if one believes that large-scale quantum computing is a technological inevitability.

\subsection{One-time pads \& key exchange over a network}

The concept of informationally secure cryptographic schemes dates back to the late 19th century. Initially developed by Frank Miller in 1882 \cite{?} and re-invented in 1917 \cite{?}, it wasn't until the 1940's that Claude Shannon actually theoretically proved the power of this technique to completely secure a transmitted message \cite{?}. To this day, one-time pads remain the only officially provable informationally secure protocol for cryptography.

This protocol is a method to encrypt information such that, \textit{if implemented perfectly} (and this is where we actually get into trouble), can never be broken. The laws of the universe and reality itself guarantee that an adversary without access to the encryption key \textit{can never}, regardless of any hypothetical computational power (quantum, classical or anything else) decrypt the message. Informationally secure protocols are the holy grail of network and information security and are of huge relevance to almost all aspects of digital life in the twenty-first century. Unfortunately, as with most things in the real world, the devil is in the details: The caveat of \textit{perfectly implemented} is essentially a practical impossibility.

The basic principles and core assumptions of one-time-pad encryption are:
\begin{itemize}
\item The sender (conventionally referred to as Alice) and receiver (Bob) both have access to a shared key that is completely random. Here we mean `random' in the information-theoretic sense of the word in that the bit strings have maximum Shannon entropy (although even this is not possible without an infinite bit string). This key has exactly same length as the message to be transmitted.
\item The key that Alice and Bob share cannot have been compromised in any way, i.e. no adversary can have any information about any part of the random bit string shared between Alice and Bob at any time.
\item This key is used once \textit{and only once} to encrypt a single message. The key or any part of the key can never be used to encrypt two separate transmissions.
\end{itemize}

If these three core points are adhered to, the encrypted message is completely unbreakable by any adversary who may intercept it, regardless of any hypothetical computational resources they may have. Unfortunately, the above conditions are simply not practical in most real world situations. 
\begin{itemize}
\item Generating a random bit string, in the true definition of random, has only become technologically possible in the past decade or two as result of quantum technology. Quantum random number generators use the intrinsic randomness of quantum mechanical processes to generate random bit strings that for all intents and purposes are sufficient for one time pads. These devices can now be bought as off the shelf units with varying degrees of quality. 
\item Avoiding the reuse of a key can, in principle, be adhered to; but satisfying this requirement may be economically or logistically impractical. Avoiding reuse becomes even more difficult when the message to be encrypted is big. There are many examples of technology in the field that require secure, high data-rate transmission. Video footage from helicopters or drones is a good example. A drone equipped with a high-resolution 4K camera system needs to be able to transmit information at a rate of 764 GB/hour uncompressed. This would require the same rate of one-time-pad material to be generated and shared between Alice and Bob to ensure a secure connection of the video stream. None of this material could be used even a second time. 
\item The third and most vulnerable constraint is the sharing of key information between Alice and Bob in a manner that can be guaranteed to have never been compromised. This is complicated by the fact that Alice and Bob in almost all practical situations will not be in physical contact with each other prior to sharing an encrypted message. How can we exchange a large amount of key material between two parties who have never met in such a way that we can be as certain as humanly possible that the key information was not revealed, sold, copied or otherwise accessed by a third party? The third party may even be authorised to have access to the key information. This would immediately destroy the \textit{perfectly implemented} assumption underlying the security of the one-time-pad. 
\end{itemize}

While many crypto-systems are not based on one-time-pad encryption because of these constraints, the sharing of cryptographic keys is still of major concern. Transmitting keys over \textit{any} publicly accessible network is fraught with security problems as there is no way of encrypting the key material without then asking how the keys used to encrypt the keys are shared.

For extremely sensitive tasks, key-exchange and security is usually achieved through some combination of segregated networking and obfuscation. Here are some examples:

\subsubsection{Security through obfuscation}

Some techniques for key and message exchange attempt to hide from adversaries any evidence that such protocols are taking place. This may be as simple as giving a secret key or message to a 20-something hipster riding a bike instead of man in a well-tailored suit with dark sunglasses and a briefcase handcuffed to his wrist. Security through obfuscation is more focused on not arousing suspicion or misdirecting adversaries to use a false attack vector when attempting to compromise information exchange, rather than directly defending against a potential attack.

\subsubsection{Security through segregated networks}

Segregating classical networks from the public and/or potential adversaries is a more common technique simply because the speed and range of radio signals and optic fibre technology is so large. Ensuring that a military or intelligence network is not connected to anything that is more widely accessible, in principle, allows for a higher level of security and the ability to have confidence that cryptographic keys can be sent without interception.

These basic techniques are rarely implemented in isolation. Complex network security uses many combinations of good encryption, segregated networks, obfuscation and other techniques to lower the probability of compromised data transmission. However, none of these techniques fully satisfy the assumptions of an information-theoretically secure cryptographic protocol, and they often rely heavily on the honesty and competence of human personnel in order to be implemented effectively.

\subsection{QKD versus classical key exchange techniques}

A 2016 assessment from the UK agency GCHQ references four concerns with QKD (Quantum Key Distribution) as an effective replacement for classical techniques.

These concerns are:
\begin{itemize}
\item \textit{QKD protocols address only the problem of agreeing on keys for encrypting data.} Ubiquitous on-demand modern services (such as verifying identities and data integrity, establishing network sessions, providing access control, and automatic software updates) rely more on authentication and integrity mechanisms — such as digital signatures — than on encryption.
\item \textit{The two major functional limitations of commercial QKD systems are the relatively short effective range of transmission and the fact that BB84 and similar proposals are fundamentally point-to-point protocols.} This means that QKD does not integrate easily with the Internet or with the mobile technologies, apps and services that dominate public and business life today.
\item \textit{Hardware is relatively expensive to obtain and maintain.} Unlike software, hardware cannot be patched remotely or cheaply when it degrades or when vulnerabilities are discovered.
\item \textit{Any real-world QKD system will be built from classical components, such as sources, detectors, fibres, and ancillary classical network devices, any one of which may prove to be a weak link.} A number of attacks have been proposed and demonstrated on deployed QKD systems that subvert one of more of these hardware components, enabling the secret shared key to be recovered without triggering an alarm.
\item \textit{Denial of service (DoS) attacks that interfere with the paths carrying the QKD transmissions also seem potentially easier with QKD than with contemporary Internet or mobile network technologies.} Since QKD devices typically abort a key establishment session when they detect tampering, this makes it difficult to recommend QKD for contexts where DoS attacks are likely to be attempted.
\end{itemize}

As we will describe, a Sneakernet based system can address each of these concerns or significantly mitigate these chief concerns of a quantum-based key distribution network.

\subsection{Trusted couriers and one-time-pads}

Before detailing the specifics of a Sneakernet based entanglement distribution network, let us first discuss the general framework that this system leverages in the context of key distribution and encryption. This is the principle of physical trusted couriers and one-time-pads. This general technique, utilised routinely for extremely sensitive key exchange, does not transmit key material over any classical network and instead entrusts a physical courier with pre-loaded key material on a portable memory stick.

The key material, which is generated at home base, is physically couriered to its destination and security is, in principle, achieved using a combination of obfuscation, deception and the trust of the courier. The couriers themselves can be heavily vetted, achieving the highest levels of security clearance within an organisation and dummy key material may be given to couriers at random to see if it is showing up in places where it is not supposed to.

Today's technology makes the other requirements -- easy access to high capacity storage and one-time-pad material of sufficient quantity to encrypt the largest-data-rate applications -- straightforward to achieve. Consequently, distribution of the key material itself is typically the hardest assumption to satisfy when relying on the information-secure nature of one-time-pads.

A quantum Sneakernet is a technological solution to the problem of having to trust the courier. We exploit the nature of quantum to develop an analogue of the trusted-courier network wherein the human couriers are no longer a weak link.

\subsection{An active quantum memory unit}

The key technology for a quantum Sneakernet is the fabrication and packaging of a long-lived \textit{active} quantum memory. Quantum memories are inherently fragile due to quantum decoherence induced via uncontrollable interactions with the wider environment. Today's best physical qubits typically have lifetimes of the order of one millisecond. While there has been significant research into finding or engineering quantum systems with lifetimes of seconds or minutes, these systems are hard to control (i.e. difficult to read in/out actual quantum information) because they have been engineered to be so isolated from the environment that the control signals required to load, manipulate or measure quantum information are difficult to implement. The ability to build quantum technology that is useful in the field requires increasing the effective memory time -- the lifetime of data stored as qubits -- so that they can be used on timescales relevant to human manipulation.

The problem of increasing the effective lifetime of qubit information was solved with the formulation of active quantum error correction (QEC) protocols. QEC utilises redundant encoding, wherein a single \textit{logical} qubit of quantum information is encoded using a finite number of \textit{physical} qubits. Continuous operations on this array of physical qubits are used to extract information regarding physical errors; and, provided physical error rates are sufficiently low, the logically encoded information can be preserved for an arbitrary amount of time. Unlike specially engineered quantum systems that are isolated to achieve long memory times, these encoded memories consist of intrinsically unstable physical qubits. However, encoded information in the system is maintained for arbitrary timescales via active QEC. Active quantum memories form the foundational building blocks of a quantum Sneakernet network, allowing us to maintain encoded quantum information for long periods -- even decades -- indeed, times long enough for most important real-world applications.

The second major element to a Sneakernet network is \textbf{PORTABILITY}. The underlying qubit technology has to be amenable to constructing active quantum memories that can be packaged and physically moved from place to place.

If we consider the six major \textit{qubit} technologies that are the most developed and have been most successful in attracting significant private/public sector investment, we see consider some of the pros and cons. In a lot of systems, \textit{infrastructure requirements} appears to be the biggest barrier to portability. 
\begin{itemize}
\item \textbf{Superconducting qubits} require operational temperatures of approximately 30mK in order to maintain operational coherence. This temperature requires dilution refrigeration technology which is difficult to make portable. 
\item \textbf{Ion-Traps} require an almost perfect vacuum environment which again may prove to be problematic. 
\item \textbf{Linear optical technology}: Can avoid infrastructure issues such as vacuums and extremely low temperatures. However, the probabilistic gates in linear optics and the consequently, ability to create active error corrected logical qubits has some practical issues to still overcome.  
\item \textbf{Quantum Dots}: Similar to superconducting technology -- dilution refrigeration technology is required.
\item \textbf{Phosphorus in Silicon}: Similar to quantum dots and superconductors -- dilution refrigeration technology is required. 
\item \textbf{Colour centres, e.g. NV-diamond}: Vacuums and dilution refrigeration technology not required. 
\end{itemize}
